Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
yufei

We will first prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$. For this purpose, given any segment $h \in \dcross_H(\bm{t})$, we will show that $h$ crosses $r^*$. To do so, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$.
\begin{itemize}
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

@@

Next, assuming that the segments of $\cross_H(r^*)$ are sorted in ascending order of their y-coordinates,
we will prove that $\dcross_H(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent statement:

>>>>

Firstly, we will prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$. For this purpose, given any segment $h \in \dcross_H(\bm{t})$, we will show that $h$ crosses $r^*$. To do so, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$.
\begin{itemize}
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

@@

Secondly, assuming that the segments of $\cross_H(r^*)$ are sorted in ascending order of their y-coordinates,
we will prove that $\dcross_H(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent statement:
